IntelliLog20160323
===================

This a log for a free adaptation which started on the 23/03/2016 with  
Wild type mice.

This R markdown requires ggplot2 package and will install it if it doesn't exist.  
```{r, echo=FALSE}
#check if ggplot exists and install it if not
list.of.packages <- c("ggplot2")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

It read the "animals.txt", "visits.txt" and "nosepokes.txt" files,    
```{r, echo = FALSE}
#Read the intellicage data, nosepokes, visits, and animals
sessionPath <- "Sessions/2016-03-23 13.57.10/"
visits <- read.csv(paste0(sessionPath,"IntelliCage/Visits.txt"), sep = "\t")
nosepokes <- read.csv(paste0(sessionPath,"IntelliCage/Nosepokes.txt"), sep = "\t")
animals <- read.csv(paste0(sessionPath,"/Animals.txt"), sep = "\t")
```
and assigns animal name for each event as a factor(visit and nosepoke).  

```{r, echo = FALSE}
#Replace AnimalTag with its AnimalName
visits$AnimalName <- lapply(visits$AnimalTag,
                                function(x){
                                            animals$AnimalName[animals$AnimalTag == x ]})
visits <- transform(visits, AnimalName = unlist(AnimalName))

#Assigning an animal name to each visit id in the nosepokes data set
nosepokes$AnimalName <- lapply(nosepokes$VisitID,
                               function(x){
                                       visits$AnimalName[visits$VisitID
                                                         == x ]})
nosepokes <- transform(nosepokes, AnimalName = unlist(AnimalName))

```

This is the visit count with the appropriate plot  
```{r, echo = TRUE}
#Plots visit count per animal
visitsCountPlot <- ggplot(visits, aes(AnimalName)) +
                   geom_bar() +
                   xlab("") +
                   ggtitle("visits Count")
print(table(visits$AnimalName))
plot(visitsCountPlot)
```

Visits over time for each animal   
```{r, fig.width=10, fig.height=4, echo = TRUE}
#plot visits over time using the ggplot2 package
visitPoints <- geom_point(aes(x = as.POSIXct(visits$Start),
                              y = visits$AnimalName,
                              colour = visits$AnimalName),
                              alpha = 0.3)
visitPointsPlot <- ggplot() +
                   visitPoints +
                   xlab("") +
                   ylab("") +
                   ggtitle("Visits") +
                   theme(legend.title=element_blank())
plot(visitPointsPlot)
```

Visit count across absoulute time  
```{r, echo = TRUE}
#create a data frame for visit per hour
hours <- vapply(split(1:nrow(visits),
                      format(as.POSIXlt(visits$Start),"%Y-%m-%d%H:00:00",tz='UTC')),
                      length,
                      0)
visitsPerHour <- as.numeric(hours)
hour <- as.POSIXct(names(hours))
visitCount <- data.frame(hour,visitsPerHour)
#Plot a line plot for the visitCount data frame
visitCountLine <- ggplot(visitCount, aes(hour, visitsPerHour)) +
                  geom_line() +
                  ylab("Count") +
                  xlab("") +
                  ggtitle("Visit count per hour")
plot(visitCountLine)
```

This is the hour with the maximun number of visits  
```{r, echo = TRUE}
print(visitCount$hour[which.max(visitCount$visitsPerHour)])
```


This is the nosepokes count with the appropriate plot 
```{r, echo = TRUE}
#Plots nosepoke count per animal
nosepokesCountPlot <- ggplot(nosepokes, aes(AnimalName)) +
                      geom_bar() +
                      xlab("") +
                      ggtitle("Nosepokes Count")
print(table(nosepokes$AnimalName))
plot(nosepokesCountPlot)
```


Nosepokes over time for each animal
```{r, fig.width=10, fig.height=4, echo = TRUE}
#Plot Nosepokes over time using the ggplot2 package
nosepokePoints <- geom_point(aes(x = as.POSIXct(nosepokes$Start),
                                 y = nosepokes$AnimalName,
                                 colour = nosepokes$AnimalName),
                                 alpha = 0.15)
nosepokesPointsPlot <- ggplot() +
                       nosepokePoints +
                       xlab("") +
                       ylab("") +
                       ggtitle("Nosepokes") +
                       theme(legend.title=element_blank())
plot(nosepokesPointsPlot)
```


  

