nosepokeAdapLog20160330
=======================

This is a log for the first nosepoke adaptation with wild types, no injections * with * light cue, the door can be opened when nosepoked in the time window of 19:00-23:59

This R markdown requires ggplot2 package and will install it if it doesn't exist.  
```{r, echo=FALSE}
#check if ggplot exists and install it if not
list.of.packages <- c("ggplot2")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

It read the "animals.txt", "visits.txt" and "nosepokes.txt" files, from both the 30 and 31 and attaches them, cause there has been a malfunction in the morning of the 31 which caused a split into two session folders.    
```{r, echo = FALSE}
#Read the intellicage data, nosepokes, visits, and animals
#Attach the 2016-03-31 15.57.42 session.
sessionPath <- "Sessions/2016-03-30 17.12.42/"
sessionPath2 <- "Sessions/2016-03-31 15.57.42/"
visits <- read.csv(paste0(sessionPath,"IntelliCage/Visits.txt"), sep = "\t")
nosepokes <- read.csv(paste0(sessionPath,"IntelliCage/Nosepokes.txt"), sep = "\t")
visits2 <- read.csv(paste0(sessionPath2,"IntelliCage/Visits.txt"), sep = "\t")
visits2$VisitID <- length(visits$VisitID) + visits2$VisitID
nosepokes2 <- read.csv(paste0(sessionPath2,"IntelliCage/Nosepokes.txt"), sep = "\t")
nosepokes2$VisitID <- length(visits$VisitID) + nosepokes2$VisitID
animals <- read.csv(paste0(sessionPath,"/Animals.txt"), sep = "\t")
visits <- rbind(visits, visits2)
nosepokes <- rbind(nosepokes, nosepokes2)
```
and assigns animal name for each event as a factor(visit and nosepoke).  

```{r, echo = FALSE}
#Replace AnimalTag with its AnimalName
visits$AnimalName <- lapply(visits$AnimalTag,
                                function(x){
                                            animals$AnimalName[animals$AnimalTag == x ]})
visits <- transform(visits, AnimalName = unlist(AnimalName))

#Assigning an animal name to each visit id in the nosepokes data set
nosepokes$AnimalName <- lapply(nosepokes$VisitID,
                               function(x){
                                       visits$AnimalName[visits$VisitID  
                                                         == x ]})
nosepokes <- transform(nosepokes, AnimalName = unlist(AnimalName))

```

This is the visit count with the appropriate plot  
```{r, echo = FALSE}
#Plots visit count per animal
visitsCountPlot <- ggplot(visits, aes(AnimalName)) +
                   geom_bar() +
                   xlab("") +
                   ggtitle("visits Count")
print(table(visits$AnimalName))
plot(visitsCountPlot)
```

Visits over time for each animal   
```{r, fig.width=10, fig.height=4, echo = FALSE}
#plot visits over time using the ggplot2 package
visitPoints <- geom_point(aes(x = as.POSIXct(visits$Start),
                              y = visits$AnimalName,
                              colour = visits$AnimalName),
                              alpha = 0.3)
visitPointsPlot <- ggplot() +
                   visitPoints +
                   xlab("") +
                   ylab("") +
                   ggtitle("Visits") +
                   theme(legend.title=element_blank())
plot(visitPointsPlot)
```

Visit count across absoulute time  
```{r, echo = FALSE}
#Count visits per hour for each animal
animalDat <- split(visits, visits$AnimalName)
visitHourAnimal <- sapply(animalDat, 
                          function(x){vapply(split(1:nrow(x),
                                            format(as.POSIXlt(x$Start),
                                                   "%Y-%m-%d%H:00:00",
                                                    tz='UTC')),
                                            length,
                                            0)},
                          simplify = "array")
visitHourAnimal <- unlist(visitHourAnimal)
visitHourAnimalDF <- read.table(text = names(visitHourAnimal), sep = ".")
visitHourAnimalDF$VisitCount <- as.numeric(visitHourAnimal)
names(visitHourAnimalDF) <- c("AnimalName", "Hour", "VisitCount")
visitHourAnimalDF$Hour <- as.POSIXct(visitHourAnimalDF$Hour)
```

```{r, echo = FALSE, fig.width = 12, fig.height = 6}
visitLines <- ggplot(visitHourAnimalDF,
                     aes(Hour, VisitCount, colour = AnimalName))
visitCountPlot <- visitLines + geom_line()
print(visitCountPlot)
```

```{r, echo = FALSE}
#create a data frame for visit per hour
hours <- vapply(split(1:nrow(visits),
                      format(as.POSIXlt(visits$Start),"%Y-%m-%d%H:00:00",tz='UTC')),
                      length,
                      0)
visitsPerHour <- as.numeric(hours)
hour <- as.POSIXct(names(hours))
visitCount <- data.frame(hour,visitsPerHour)
#Plot a line plot for the visitCount data frame
visitCountLine <- ggplot(visitCount, aes(hour, visitsPerHour)) +
                  geom_line() +
                  ylab("Count") +
                  xlab("") +
                  ggtitle("Visit count per hour")
```

This is the hour with the maximun number of visits  
```{r, echo = FALSE}
print(visitCount$hour[which.max(visitCount$visitsPerHour)])
```


This is the nosepokes count with the appropriate plot 
```{r, echo = FALSE}
#Plots nosepoke count per animal
nosepokesCountPlot <- ggplot(nosepokes, aes(AnimalName)) +
                      geom_bar() +
                      xlab("") +
                      ggtitle("Nosepokes Count")
print(table(nosepokes$AnimalName))
plot(nosepokesCountPlot)
```


Nosepokes over time for each animal
```{r, fig.width=10, fig.height=4, echo = FALSE}
#Plot Nosepokes over time using the ggplot2 package
nosepokePoints <- geom_point(aes(x = as.POSIXct(nosepokes$Start),
                                 y = nosepokes$AnimalName,
                                 colour = nosepokes$AnimalName),
                                 alpha = 0.15)
nosepokesPointsPlot <- ggplot() +
                       nosepokePoints +
                       xlab("") +
                       ylab("") +
                       ggtitle("Nosepokes") +
                       theme(legend.title=element_blank())
plot(nosepokesPointsPlot)
```

Check that drinking occoured only in the 19:00 23:59 time window, it shows the nosepokes where atleast one lick had happend, horizontal lines show the time window were the corner is active.
```{r, echo = FALSE, fig.width=10, fig.height=4}
#Plot licks over time using the ggplot2 package
lickIdx <- (nosepokes$LickNumber > 0)
lickPoints <- geom_point(aes(x =as.POSIXct(nosepokes$Start[lickIdx]),
                                 y = nosepokes$AnimalName[lickIdx],
                                 colour = nosepokes$AnimalName[lickIdx]),
                                 alpha = 0.3)
lickPointsPlot <- ggplot() +
                       lickPoints +
                       xlab("") +
                       ylab("") +
                       ggtitle("Nosepokes with at least one lick") +
                       theme(legend.title=element_blank())
plot(lickPointsPlot)

```


This is a plot showing the amount of nosepokes in the time window per day per animal  
```{r, echo = FALSE}
#find all the nosepokes which occoured in the time windows
library(lubridate)
hourNosepokes <- hour(ymd_hms(as.POSIXct(nosepokes$Start)))
inds <- 1:max(which(hourNosepokes == 23)) #indices of nosepokes in days                                            #with window                 
hourNosepokes <- hourNosepokes[inds]
windowNosepokes <- nosepokes[inds,]
dayNosepokes <- day(ymd_hms(as.POSIXct(
                    windowNosepokes$Start)))
windowNosepokes$Day <- dayNosepokes
windowNosepokes$Hour <- hourNosepokes
startHour <- 19
endHour <- 23
windowNosepokes <- windowNosepokes[windowNosepokes$Hour >= startHour &
                                   windowNosepokes$Hour <= endHour,]
p1 <- ggplot(windowNosepokes, aes(Day, fill=AnimalName)) +
        geom_bar() +
        ggtitle("Inside the time window nosepoke count")
```

This is the count of nosepokes per day per animal in the time windows
```{r, echo = FALSE}
#make a data frame with the count of nosepokes in the time window for each day for each animal
name <- rep(animals$AnimalName,
            length(unique(windowNosepokes$Day)))
day <- rep(unique(windowNosepokes$Day),
           length(animals$AnimalName))

animalWindowNosepokesCount <- data.frame(name, day, startHour, endHour)
names(animalWindowNosepokesCount) <- c("AnimalName", "Day", "startHour", "endHour")
c <- as.numeric()
for(i in 1:nrow(animalWindowNosepokesCount)){
        animalWindowNosepokesCount$Count[i] <-
                sum((windowNosepokes$AnimalName ==
                   animalWindowNosepokesCount$AnimalName[i]) &
                   (windowNosepokes$Day ==
                   animalWindowNosepokesCount$Day[i]) &
                   (windowNosepokes$Hour <=
                   animalWindowNosepokesCount$endHour[i]) &
                   (windowNosepokes$Hour >=
                   animalWindowNosepokesCount$startHour[i]))
}
p2 <- ggplot(animalWindowNosepokesCount,
             aes(Day, Count, group = AnimalName, colour = AnimalName)) +       geom_line() +
      geom_point() +
      ggtitle("Nosepokes in 19:00-23:59 ")
print(p2)
print(animalWindowNosepokesCount[,-c(3,4)])
```
