TrainingLog20160401
=======================

This is a log for the first training session with wild types, no injections, the door can be opened when nosepoked in the time window of 19:00-23:59, but only after a light cue appears between 2-4s after a visit occours.

This R markdown requires ggplot2 package and will install it if it doesn't exist.  
```{r, echo=FALSE}
#check if ggplot exists and install it if not
list.of.packages <- c("ggplot2")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

It read the "animals.txt", "visits.txt" and "nosepokes.txt" files, removes all non-first nosepokes    
```{r, echo = FALSE}
#Read the intellicage data, nosepokes, visits, and animals
sessionPath <- "Sessions/2016-04-01 17.01.25/"
visits <- read.csv(paste0(sessionPath,"IntelliCage/Visits.txt"), sep = "\t")
nosepokes <- read.csv(paste0(sessionPath,"IntelliCage/Nosepokes.txt"), sep = "\t")
#remove the nosepokes from the right side
nosepokes <- nosepokes[!nosepokes$SideError,]
#Keep only the first nosepoke in each visit
nosepokes <- nosepokes[!duplicated(nosepokes$VisitID),]

animals <- read.csv(paste0(sessionPath,"/Animals.txt"), sep = "\t")
```
and assigns animal name for each event as a factor(visit and nosepoke).  

```{r, echo = FALSE}
#Replace AnimalTag with its AnimalName
visits$AnimalName <- lapply(visits$AnimalTag,
                                function(x){
                                            animals$AnimalName[animals$AnimalTag == x ]})
visits <- transform(visits, AnimalName = unlist(AnimalName))

#Assigning an animal name to each visit id in the nosepokes data set
nosepokes$AnimalName <- lapply(nosepokes$VisitID,
                               function(x){
                                       visits$AnimalName[visits$VisitID  
                                                         == x ]})
nosepokes <- transform(nosepokes, AnimalName = unlist(AnimalName))

```

This is the visit count with the appropriate plot  
```{r, echo = FALSE}
#Plots visit count per animal
visitsCountPlot <- ggplot(visits, aes(AnimalName)) +
                   geom_bar() +
                   xlab("") +
                   ggtitle("visits Count")
print(table(visits$AnimalName))
plot(visitsCountPlot)
```

Visits over time for each animal   
```{r, fig.width=10, fig.height=4, echo = FALSE}
#plot visits over time using the ggplot2 package
visitPoints <- geom_point(aes(x = as.POSIXct(visits$Start),
                              y = visits$AnimalName,
                              colour = visits$AnimalName),
                              alpha = 0.3)
visitPointsPlot <- ggplot() +
                   visitPoints +
                   xlab("") +
                   ylab("") +
                   ggtitle("Visits") +
                   theme(legend.title=element_blank())
plot(visitPointsPlot)
```

Visit count across absoulute time  
```{r, echo = FALSE}
#Count visits per hour for each animal
animalDat <- split(visits, visits$AnimalName)
visitHourAnimal <- sapply(animalDat, 
                          function(x){vapply(split(1:nrow(x),
                                            format(as.POSIXlt(x$Start),
                                                   "%Y-%m-%d%H:00:00",
                                                    tz='UTC')),
                                            length,
                                            0)},
                          simplify = "array")
visitHourAnimal <- unlist(visitHourAnimal)
visitHourAnimalDF <- read.table(text = names(visitHourAnimal), sep = ".")
visitHourAnimalDF$VisitCount <- as.numeric(visitHourAnimal)
names(visitHourAnimalDF) <- c("AnimalName", "Hour", "VisitCount")
visitHourAnimalDF$Hour <- as.POSIXct(visitHourAnimalDF$Hour)
```

```{r, echo = FALSE, fig.width = 12, fig.height = 6}
visitLines <- ggplot(visitHourAnimalDF,
                     aes(Hour, VisitCount, colour = AnimalName))
visitCountPlot <- visitLines + geom_line()
print(visitCountPlot)
```

```{r, echo = FALSE}
#create a data frame for visit per hour
hours <- vapply(split(1:nrow(visits),
                      format(as.POSIXlt(visits$Start),"%Y-%m-%d%H:00:00",tz='UTC')),
                      length,
                      0)
visitsPerHour <- as.numeric(hours)
hour <- as.POSIXct(names(hours))
visitCount <- data.frame(hour,visitsPerHour)
#Plot a line plot for the visitCount data frame
visitCountLine <- ggplot(visitCount, aes(hour, visitsPerHour)) +
                  geom_line() +
                  ylab("Count") +
                  xlab("") +
                  ggtitle("Visit count per hour")
```

This is the hour with the maximun number of visits  
```{r, echo = FALSE}
print(visitCount$hour[which.max(visitCount$visitsPerHour)])
```


This is the nosepokes count with the appropriate plot 
```{r, echo = FALSE}
#Plots nosepoke count per animal
nosepokesCountPlot <- ggplot(nosepokes, aes(AnimalName)) +
                      geom_bar() +
                      xlab("") +
                      ggtitle("Nosepokes Count")
print(table(nosepokes$AnimalName))
plot(nosepokesCountPlot)
```


Nosepokes over time for each animal
```{r, fig.width=10, fig.height=4, echo = FALSE}
#Plot Nosepokes over time using the ggplot2 package
nosepokePoints <- geom_point(aes(x = as.POSIXct(nosepokes$Start),
                                 y = nosepokes$AnimalName,
                                 colour = nosepokes$AnimalName),
                                 alpha = 0.15)
nosepokesPointsPlot <- ggplot() +
                       nosepokePoints +
                       xlab("") +
                       ylab("") +
                       ggtitle("Nosepokes") +
                       theme(legend.title=element_blank())
plot(nosepokesPointsPlot)
```

Check that drinking occoured only in the 19:00 23:59 time window, it shows the nosepokes where atleast one lick had happend, horizontal lines show the time window were the corner is active.
```{r, echo = FALSE, fig.width=10, fig.height=4}
#Plot licks over time using the ggplot2 package
lickIdx <- (nosepokes$LickNumber > 0)
lickPoints <- geom_point(aes(x =as.POSIXct(nosepokes$Start[lickIdx]),
                                 y = nosepokes$AnimalName[lickIdx],
                                 colour = nosepokes$AnimalName[lickIdx]),
                                 alpha = 0.3)
lickPointsPlot <- ggplot() +
                       lickPoints +
                       xlab("") +
                       ylab("") +
                       ggtitle("Nosepokes with at least one lick") +
                       theme(legend.title=element_blank())
plot(lickPointsPlot)

```


This is a plot showing the amount of nosepokes in the time window per day per animal  
```{r, echo = FALSE}
#find all the nosepokes which occoured in the time windows
library(lubridate)
hourNosepokes <- hour(ymd_hms(as.POSIXct(nosepokes$Start)))
inds <- 1:max(which(hourNosepokes == 23)) #indices of nosepokes in days                                            #with window                 
hourNosepokes <- hourNosepokes[inds]
windowNosepokes <- nosepokes[inds,]
dayNosepokes <- day(ymd_hms(as.POSIXct(
                    windowNosepokes$Start)))
windowNosepokes$Day <- dayNosepokes
windowNosepokes$Hour <- hourNosepokes
startHour <- 19
endHour <- 23
windowNosepokes <- windowNosepokes[windowNosepokes$Hour >= startHour &
                                   windowNosepokes$Hour <= endHour,]
p1 <- ggplot(windowNosepokes, aes(Day, fill=AnimalName)) +
        geom_bar() +
        ggtitle("Inside the time window nosepoke count")
```

This is the count of nosepokes per day per animal in the time windows
```{r, echo = FALSE}
#make a data frame with the count of nosepokes in the time window for each day for each animal
name <- rep(animals$AnimalName,
            length(unique(windowNosepokes$Day)))
day <- rep(unique(windowNosepokes$Day),
           length(animals$AnimalName))

animalWindowNosepokesCount <- data.frame(name, day, startHour, endHour)
names(animalWindowNosepokesCount) <- c("AnimalName", "Day", "startHour", "endHour")

#Set Start and End colums in data as postixct
windowNosepokes$Start <- as.POSIXct(windowNosepokes$Start) 
windowNosepokes$End <- as.POSIXct(windowNosepokes$End)
visits$Start <- as.POSIXct(visits$Start)

#Check if a after time error has occoured and update windowNosepokes
windowNosepokes$TimeError[
        afterTimeErrorInds(visits, windowNosepokes)] <- 1 

for(i in 1:nrow(animalWindowNosepokesCount)){
        animalWindowNosepokesCount$Count[i] <-
                sum((windowNosepokes$AnimalName ==
                   animalWindowNosepokesCount$AnimalName[i]) &
                   (windowNosepokes$Day ==
                   animalWindowNosepokesCount$Day[i]) &
                   (windowNosepokes$Hour <=
                   animalWindowNosepokesCount$endHour[i]) &
                   (windowNosepokes$Hour >=
                   animalWindowNosepokesCount$startHour[i]))
        animalWindowNosepokesCount$TimeError[i] <-
                sum((windowNosepokes$AnimalName ==
                   animalWindowNosepokesCount$AnimalName[i]) &
                   (windowNosepokes$Day ==
                   animalWindowNosepokesCount$Day[i]) &
                   (windowNosepokes$Hour <=
                   animalWindowNosepokesCount$endHour[i]) &
                   (windowNosepokes$Hour >=
                   animalWindowNosepokesCount$startHour[i]) &
                   (windowNosepokes$TimeError == 1))
}
p2 <- ggplot(animalWindowNosepokesCount,
             aes(Day, Count, group = AnimalName, colour = AnimalName)) +       geom_line() +
      geom_point() +
      ggtitle("Nosepokes in 19:00-23:59 ")
print(p2)
```

This is a plot showing the fraction of errors per time window.
```{r, echo = FALSE}
p3 <- ggplot(animalWindowNosepokesCount,
             aes(Day,
                 TimeError/Count,
                 group = AnimalName,
                 colour = AnimalName)) +
        geom_line() +
        geom_point() +
      ggtitle("Error fraction per day")
print(p3)
print(animalWindowNosepokesCount[,-c(3,4)])
```
The data shows that there are times when they succeed in the task, but do not lick, or that the lickometer doesn't record the licking. We are trying to make the task easier so they could learn and drink.  
